Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models By Using Data of Pollsters From Five Thirty Eight In 2024

### 2024-10-23 paper/paper.qmd
new render pdf

To get a prediction by the Vayesian model we have, we first spline fit the model, and then create a data frame and generate posterior predictions by the new data frame.
## Spline Fit for Bayesian model set-up

We run the model in R [@citeR] using the `rstanarm` package of [@rstanarm]. We use priors $\text{Normal}(0, 5)$ to allow for more flexibility of predictors effects with “autoscale = TRUE”. Then we crate a data frame like [@tbl-newdata], we set the quality scale of predict data to the best to perform a poll that has high quality. the result is shown as [@sec-splresult]
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-newdata

>>>>

To get a prediction by the Bayesian model we have, we first spline fit the model, and then create a data frame and generate posterior predictions by the new data frame.

## Spline Fit for Bayesian model set-up
We run the model in R [@citeR] using the `rstanarm` package of [@rstanarm]. We use priors $\text{Normal}(0, 5)$ to allow for more flexibility of predictors effects with “autoscale = TRUE”. Then we crate a data frame like [@tbl-newdata], we set the quality scale of predict data to the best to perform a poll that has high quality. the result is shown as [@sec-splresult]
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-newdata
